``FISTA'' in Banach spaces with adaptive discretisations

### 2021-10-05 response.tex

	\item \review{page 10 line 21 and 38 typos: Sectoin and although although}

	These typos have been corrected.

	\item \review{page 10 line 36: In the infinite-dimensional context, I think it is clear what the authors mean with $\lVert\cdot\rVert_1$. They clearly state it as TV in (15), but it is a bit misleading especially later when they use $\lVert\cdot\rVert_\infty$.}

	This has been clarified in the text, now equations (15) and (20)-(21). The $\lVert\cdot\rVert_\infty$ only appears as the dual-norm of our ${\vert\kern-0.25ex\vert\kern-0.25ex\vert \cdot \vert\kern-0.25ex\vert\kern-0.25ex\vert}$.

@@

	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions. While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. You were right, the former foundations were not rigorous enough. We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space. The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space. Consequently, we also realised that the orthogonal projection was not required either, we now allow $U^n$ to be subsets of $\F H$ rather than subspaces. The Banach space setting is reserved for examples discussed in Section 5 onwards.

@@

	\item \review{Does (5) imply strong or weak lower semicontinuity of $g$?}

	$g$ only needs to be weakly lower-semicontinuous for the existence of minimisers. This is now clarified further in the text (now equation (4)).

	\item \review{Lemma 1: There is no Lemma 1 in [10]}

	We apologise for the mistake, the numbering has now been corrected.

### 2021-10-05 paper.tex
New results and explanation

	\subsubsection{Single iterations}
	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
		\Copy{thm: descent lemma}{
			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
		}
	\end{lemma}
	\noindent This is exactly the result of \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$. Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.

@@

	\paragraph{Numerical results}
	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom. \edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Figure~\ref{fig: haar data}. All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$. The gradient metric shown throughout is the $\ell^2$ norm. Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that 
	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).

	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive algorithms as shown in Figure~\ref{fig: convergence with method}. In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower. \edit{}{Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time. }

>>>>

	\subsubsection{Single iterations}
	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
		\Copy{thm: descent lemma}{
			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
		}
	\end{lemma}
	\noindent The proof is exactly the same as in \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$. Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.

@@

	\paragraph{Numerical results}
	We consider two phantoms where the ground-truth is either a binary disc or the Shepp-Logan phantom. \edit{No noise is added to the Shepp-Logan data but 5\% Gaussian white noise is added to the disc data.}{Both examples are corrupted with \SI{2}{\percent} Laplace distributed noise.} This is visualised in Figure~\ref{fig: haar data}. All optimisations shown are spatially adaptive using Haar wavelets and initialised with $\spcf0^0= \{\varx0\mapsto c\st c\in\F R\}$. The gradient metric shown throughout is the $\ell^\infty$ norm. Motivated by \eqref{eq: wavelet error metric}, the spatial adaptivity is chosen to refine nodes $j\in\op{leaf}(J_n)$ to ensure that 
	$$ \norm{\1_{\supp(w_j)}\A^*\vvard0_n}_{L^2} -\mu  \leq 10\Norm{\partial_n\op{E}(\varf0_n)}_*$$
	for all $j$ and $n$ (i.e. so that the continuous gradient is less than 10 times the discrete gradient).
	\edit{}{We do not expect wavelet regularisation to have state-of-the-art performance in the examples of Figure~\ref{fig: haar data}. What they demonstrate is the preference Haar wavelets have to align large discontinuities with a coarse grid, even when the discretisation is allowed to be as fine as necessary. There is an average of $2\cdot10^6$ wavelet coefficients in each discretised reconstruction, although the higher frequencies have much smaller intensities. In limited data scenarios, wavelet regularisation automatically selects a local `resolution' which reflects the quality of data. Particularly in the Shepp-Logan reconstruction, we see that the outer ring is detected with a finer precision than the dark interior ellipses.}

	The first numerical results shown in Figure~\ref{fig: haar convergence} compare the same adaptive FISTA variants as shown in Figure~\ref{fig: convergence with method}. In these examples we see that the greedy FISTA and the $a=20$ algorithms achieve almost linear convergence while $a=2$ is significantly slower. \edit{}{Interestingly, in both examples the $a=20$ variant uses half as many wavelets as the Greedy variant, and therefore converges slightly faster in time. }
